Monte Carlo for all parameters

### 2024-07-25 MC_all.Rmd
More global MC and function for local variables

```{r}
# Importing the database with the artificial forest
trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
```

@@

@@

  for (b in 1:B) { # All in one "for" loop
    # Uniform sampling over the whole territory
    a1 <- runif(n, 0, 1000)
    a2 <- runif(n, 0, 1000)
    # Variables of interest derived from the sample
    var_nb <- mapply(circle_nb, a1, a2)
    var_vol <- mapply(circle_vol, a1, a2)
    MC_b <- data.frame(x = a1, y = a2, z = var_nb, t = var_vol)
    MC_df <- cbind(MC_df, MC_b)
    colnames(MC_df)[4*(b-1)+2] <- paste("x", b, sep = "")
    colnames(MC_df)[4*(b-1)+2+1] <- paste("y", b, sep = "")
    colnames(MC_df)[4*(b-1)+2+2] <- paste("nb", b, sep = "")
    colnames(MC_df)[4*(b-1)+2+3] <- paste("vol", b, sep = "")
    est_b <- t(data.frame(x = sum(MC_df[4*(b-1)+2+2] /p), y = sum(MC_df[4*(b-1)+2+3] /p), z = (sum(MC_df[4*(b-1)+2+3] /p))/(sum(MC_df[4*(b-1)+2+2]/p))))
    MC_est <- cbind(MC_est, est_b)
    colnames(MC_est)[b+1] <- paste("ech", b, sep = "") 
  }
  MC_df$useless <- NULL
  MC_est$useless <- NULL
  MC_var <- c(var(as.vector(t(MC_est[1,]))), var(as.vector(t(MC_est[2,]))), var(as.vector(t(MC_est[3,]))))
  return(list(MC_df, MC_est, MC_var))
}
```

@@

@@

```{r}
# Making of one estimation for each sample made by the bootstrap method
est_boot <- function(df, p){
  # df: dataframe with 3*B columns and n rows

  n <- nrow(df) + 1 # sample size of the initial sample
  nboot <- length(df)/3 # number of bootstrap samples
  vec_est <- c()
  for (c in 1:nboot) {
    vec_est <- append(vec_est, (n/(n-1))*sum(df[,3*c]/p))
    # (n/(n-1)) is the correction needed since we choose only (n-1) points
  }
  vec_est <- sort(vec_est)
  return(vec_est)
  # Vector with one estimation for each sample
}
```

@@

MC_boot <- function(n, B1, B2, f){
  # n: sample size; B1: number of iterations for MC;
  # B2: number of iterations for bootstrap;
  # f: function to consider (2 arguments)

@@

    # Bootstrap iterations
    df_boot <- f_boot(random_points, B2)
    est_boot_val <- est_boot(df_boot, p)
    var_est_boot <- append(var_est_boot, var(est_boot_val))
  }
  return(mean(var_est_boot))
  # Mean of the bootstrap variance
}
```

# First example: number of trees

@@

res1_nb <- MonteCarlo(n, 10000, circle_nb)
# Just one circle to begin with

@@

```{r}
cat("Monte Carlo variance:", res1_nb)
# Examples:
# Monte Carlo variance: 2789037
# Monte Carlo variance: 2827317
```

@@

res2_nb <- MC_boot(n, B1 = 1000, B2 = 400, f = circle_nb)
# Just one circle to begin with

@@

```{r}
cat("Mean of the variance of bootstrap samples:", res2_nb)
# Examples:
# Mean of the variance of bootstrap samples: 2845120
# Mean of the variance of bootstrap samples: 2851631
```

```{r}
cat("We get a difference of: ", 100*(max(res1_nb,res2_nb)-min(res1_nb,res2_nb))/min(res1_nb,res2_nb), "%", sep = "")
# Examples:
# We get a difference of: 2.01084%
# We get a difference of: 0.8599411%
```

>>>>

```{r}
# Importing the database with the artificial forest
all_trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
# To get closer to the NFI process, trees whose circumference is under 23.5 cm are not considered
trees <- trees[(pi*trees$d130 > 23.5),]
```

@@

```{r}
# True values
cat("Number of trees:", length(trees$x), "\nTotal volume:", sum(trees$v), "\nWhich leads to the following ratio \"Total volume / Number of trees\":", sum(trees$v)/nrow(trees))
```

@@

  for (b in 1:B) { # All in one "for" loop
    # Uniform sampling over the whole territory
    a1 <- runif(n, 0, 1000)
    a2 <- runif(n, 0, 1000)
    # Variables of interest derived from the sample
    var <- mapply(circle_all, a1, a2)
    MC_b <- data.frame(x = a1, y = a2, z = t(var)[,1], t = t(var)[,2])
    MC_df <- cbind(MC_df, MC_b)
    colnames(MC_df)[4*(b-1)+2] <- paste("x", b, sep = "")
    colnames(MC_df)[4*(b-1)+2+1] <- paste("y", b, sep = "")
    colnames(MC_df)[4*(b-1)+2+2] <- paste("nb", b, sep = "")
    colnames(MC_df)[4*(b-1)+2+3] <- paste("vol", b, sep = "")
    est_b <- t(data.frame(x = sum(MC_df[4*(b-1)+2+2] /p), y = sum(MC_df[4*(b-1)+2+3] /p), z = (sum(MC_df[4*(b-1)+2+3] /p))/(sum(MC_df[4*(b-1)+2+2]/p))))
    MC_est <- cbind(MC_est, est_b)
    colnames(MC_est)[b+1] <- paste("ech", b, sep = "") 
  }
  MC_df$useless <- NULL
  MC_est$useless <- NULL
  MC_var <- c(var(as.vector(t(MC_est[1,]))), var(as.vector(t(MC_est[2,]))), var(as.vector(t(MC_est[3,]))))
  return(list(Data = MC_df, Estimators = MC_est, Variances = MC_var))
  # Data: local variables (number and voume) for each point in each sample
  # Estimators: 3 estimators (number, volume, ratio volume / number) for each sample
  # Variances: Monte Carlo variance for each of the totals / ratio
}
```

@@

```{r}
# mean(as.vector(res_MC$Estimators[1,]))
```

```{r}
# mean(res_MC$Estimators[1,])
```

@@

```{r}
# Making of estimations for each sample made by the bootstrap method
est_boot <- function(df, p){
  # df: dataframe with 4*B columns and n rows

  n <- nrow(df) + 1 # sample size of the initial sample
  nboot <- length(df)/4 # number of bootstrap samples
  vec_est1 <- c()
  vec_est2 <- c()
  for (c in 1:nboot) {
    vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,3*c]/p))
    vec_est2 <- append(vec_est2, (n/(n-1))*sum(df[,4*c]/p))
    # (n/(n-1)) is the correction needed since we choose only (n-1) points
  }
  vec_est <- data.frame(est1 = vec_est1, est2 = vec_est2)
  return(vec_est)
  # Vector with one estimation for each sample
}
```

@@

MC_boot <- function(n, B1, B2){
  # n: sample size; B1: number of iterations for MC;
  # B2: number of iterations for bootstrap;
  # f: function to consider (2 arguments)

@@

    # Bootstrap iterations
    df_boot <- f_boot(random_points, B2)
    est_boot_val <- est_boot(df_boot, p)
    var_est_boot <- append(var_est_boot, var(est_boot_val))
  }
  return(mean(var_est_boot))
  # Variances: mean of the bootstrap variance for each estimator
}
```

# Example

@@

res1 <- MonteCarlo(n, 10000)
# Just one circle to begin with

@@

```{r}
cat("Monte Carlo means of estimators: \n - for the number of trees:", mean(as.vector(res1$Estimators[1,])), "\n - for the volume of trees:", mean(as.vector(res1$Estimators[1,])), "\n - for the ratio volume / number of trees:", mean(as.vector(res1$Estimators[1,])))
# Example:
```

```{r}
cat("Monte Carlo variance: \n - for the number of trees:", res1$Variances[1], "\n - for the volume of trees:", res1$Variances[2], "\n - for the ratio volume / number of trees:", res1$Variances[3])
# Example:
```

@@

res2 <- MC_boot(n, B1 = 1000, B2 = 400)
# Just one circle to begin with

@@

```{r}
cat("Mean of the variance of bootstrap samples:", res2_nb)
cat("Mean of the variance of bootstrap samples: \n - for the number of trees:", res2$Variances[1], "\n - for the volume of trees:", res2$Variances[2], "\n - for the ratio volume / number of trees:", res2$Variances[3])
# Examples:
# Mean of the variance of bootstrap samples: 2845120

```

```{r}
diff_percent <- function(x,y)100*(max(x,y)-min(x,y))/min(x,y)
cat("We get a difference of: ", diff_percent(), "%", sep = "")
# Examples:
# We get a difference of: 2.01084%
# We get a difference of: 0.8599411%
```
